Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-06-19 edubots_surveys.Rnw
Fixed bib
Trying to give closure to #6 linking it with the rest of the paper

Several higher education chatbots' evaluation studies were
undertaken. For instance, an evaluation review study presented by
\cite{Smutny2020} examined 47 educational chatbots implemented in
Facebook Messenger with the focus to identify characteristics and
quality metric such as language, subject matter and platform. Another
study aimed to categorise educational chatbots according to their
purpose into service-oriented and teaching-oriented
\cite{perez2020rediscovering}. The first category includes those that
provide service support such as the chatbot Ask Holly \cite{meetholly}
and Dina \cite{santoso2018dinus}, both chatbots respond to students'
questions about enrollment and registration. Ask
L.U. \cite{LancasterUniversity_2019} answers students' frequently
asked questions about timetables, grades, tutors and societies. LISA
\cite{dibitonto2018chatbot} and Differ \cite{differchat} facilitate
breaking the ice between new students by introducing them to each
other.  \cite{ranoliya2017chatbot} proposed a generic chatbot for
university students that is able to answer their frequently asked
questions; for some time, the University of Granada had ELVIRA as a
chatbot in their main page \cite{MOREO20129}. Besides being able to
answer pre-established (frequent) questions, it did so from the main
University of Granada using an inset character, voiced by a real
person, who lip-synched the answers. The emphasis in this case,
however, was on the authenticity of the synchronization more than in
making the update of questions and answers simpler, or more
interactive, using actual messaging platforms. In most cases, using
the inset search engine was able to give you more up-to-date and
accurate answers.

@@

Regarding the factors for the adoption of chatbots in higher
education, many studies have focused on the evaluation of technology
acceptance and usability \cite{Roblyer2010,Pimmer2019}. However,
higher education is a special domain where according to
\cite{hobert2019you}, specific pedagogical factors such as learning
success or increased motivation are more important.  Therefore, to
develop efficient chatbots for higher education, all stakeholders'
(i.e. educators, students, institutions, etc) expectations needs to be
carefully collected and taken into consideration
\cite{sjostrom2018designing,tsivitanidouusers}.

>>>>

Several higher education chatbots' evaluation studies were
undertaken. For instance, an evaluation review study presented by
\cite{Smutny2020} examined 47 educational chatbots implemented in
Facebook Messenger with the focus to identify characteristics and
quality metric such as language, subject matter and platform. Another
study aimed to categorise educational chatbots according to their
purpose into service-oriented and teaching-oriented
\cite{perez2020rediscovering}. The first category includes those that
provide service support such as the chatbot Ask Holly \cite{meetholly}
and Dina \cite{santoso2018dinus}, both chatbots respond to students'
questions about enrollment and registration. Ask
L.U. \cite{LancasterUniversity_2019} answers students' frequently
asked questions about timetables, grades, tutors and societies. LISA
\cite{dibitonto2018chatbot} and Differ \cite{differ.chat} facilitate
breaking the ice between new students by introducing them to each
other.  \cite{ranoliya2017chatbot} proposed a generic chatbot for
university students that is able to answer their frequently asked
questions; for some time, the University of Granada had ELVIRA as a
chatbot in their main page \cite{MOREO20129}. Besides being able to
answer pre-established (frequent) questions, it did so from the main
University of Granada using an inset character, voiced by a real
person, who lip-synched the answers. The emphasis in this case,
however, was on the authenticity of the synchronization more than in
making the update of questions and answers simpler, or more
interactive, using actual messaging platforms. In most cases, using
the inset search engine was able to give you more up-to-date and
accurate answers.

@@

As in any new technology, it's important to ascertain which factors will help or impede its adoption; this is why many studies have focused on the evaluation of technology
acceptance and usability \cite{Roblyer2010,Pimmer2019}. However,
higher education is a special domain where according to
\cite{hobert2019you}, specific pedagogical factors such as learning
success or increased motivation are more important.  Therefore, to
develop efficient chatbots for higher education, all stakeholders'
(i.e. educators, students, institutions, etc) expectations needs to be
carefully collected and taken into consideration
\cite{sjostrom2018designing,tsivitanidouusers}.

This is why this paper is focused on which factors are considered the most important by the people that are going to use them. We spread our survey over university as well as other higher education institution, so that we find out if there's any kind of difference between long-cycle, degree oriented institutions (universities) and vocational/professionally oriented institutions (elsewhere known as "polytechnics" or "vocational training" institutions, in Spain known as high schools).
